Predicting Tags for StackOverflow Posts

### 2013-03-04 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: cda8ce26309171ed784c21c2f7d3395ac480e842 [formerly 38129b4ae21918ab8eb0b3e3d8cec260a87cac1f]
Former-commit-id: 0517f534b694a2dc34e6fc07815156165b610a5f

Our StackOverflow model is a successful case showing that ACT-Rs declarative memory retrieval mechanisms scale, and can be applied to retrieval requests occurring across large-scale declarative memory datasets. 
The model can successfully tag 67\% of posts correctly, when tasked to predict one tag per post on average.
The model is also computationally space efficient:
Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of \num{556677795} chunks occur in less than one second on a single processor.
Although certainly not perfect, model accuracy is significant and retrieval times are fast, so we are considering potential applications of the model in real-world settings.

>>>>

Our StackOverflow model is a successful case showing that ACT-R's declarative memory retrieval mechanisms scale, and can be applied to retrieval requests occurring across large-scale declarative memory datasets. 
The model can successfully tag 67\% of posts correctly, when tasked to predict one tag per post on average.
The model is also computationally space efficient:
Large-scale relational database techniques and efficient sparse matrix data structures were used for implementation,
so that the data structures require only 3GB of memory and retrieval requests with a DM dataset of \num{556677795} chunks occur in less than one second on a single processor.
Although certainly not perfect, model accuracy is significant and retrieval times are fast, so we are considering potential applications of the model in real-world settings.
